---
title: Processing Ion Mobility data
author: "Oliver M. Crook"
output:
    BiocStyle::html_document:
        toc_float: true
geometry: margin = 2cm     
vignette: >
    %\VignetteIndexEntry{Processing Ion Mobility data}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
    %\VignettePackage{Spectra}
    %\VignetteDepends{Spectra,mzR,BiocStyle}
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Package**: `r Biocpkg("hdxmspro")`<br />
**Authors**: `r packageDescription("hdxmspro")[["Author"]] `<br />
**Last modified:** `r file.info("hdxmspro.Rmd")$mtime`<br />
**Compiled**: `r date()`

```{r, echo = FALSE, message = FALSE}
library(Spectra)
library(BiocStyle)
library(Biostrings)
library(ggplot2)
library(viridis)
library(patchwork)
library(IonMobility)

set.seed(1)
```

# Introduction

This vignette seeks to explain how to process Ion Mobility enabled
hydrogen deuterium exchange mass spectrometry data. Ion mobility data includes
an additional dimension for peptide separation which reduces the peptide spectra
overlap but does also mean that more peptides are resolved increasing the burdon
on computational pipelines. The `hdxmspro` package depends on the `IonMobility`
package which enables generics and methods to handle the additional dimension.

# Getting started

We load a small example dataset from the package

```{r, cache = TRUE, warning=FALSE}
data(phosb_test)
```

We can examine the object. This test object contains 10 spectra. 
Note that there are a much larger number of spectra than data
without the ion mobility dimension.
```{r,}
phosb_test
```
Additional information located in the `spectraData`:
```{r,}
spectraData(phosb_test)
```
Note, the important additional spectra variable `ionMobilityDriftTime`. 







The units here is roughly `0.054` corresponding to the `adcPusherFrequency`
```{r,}
head(phosb_test$ionMobilityDriftTime)
median(diff(phosb_test$ionMobilityDriftTime)) # estimate adcPusherFrequecy
```
The separate `IonMobility` package allow manipulation of this dimension of the
data. The following functions work similary to the other filter functions:
```{r,}
head(IonMobility::ionMobilityTime(phosb_test))
exmp <- IonMobility::filterIonMobility(phosb_test, c(0,0.5))
exmp
```
